### 2008-08-13 doc/glite_gateway/glite_gateway.tex
Reference fix
Propagated version

\def\documenttitle{The glite gateway plugins of ARCLIB and related command line tools}
\captionsetup{margin=20pt,font={footnotesize, it},labelfont=bf}
\begin{document}
\def\today{\number\day/\number\month/\number\year}
\begin{titlepage}

@@

{\raggedleft DRAFT\_NORDUGRID-TECH-22\par}

@@

The purpose of this document is to describe this gLite\cite{glite} specific plugins of the ARCLIB (...Hivatkozni: jövőbeli Deliverable) to present the related command line utilities built on top of these libraries. The gateway library together with the tools enables seemless interoparability with gLite computing elements. It is possible, that relevant sections of this document will be moved into ARC1 userguide and into ARCLIB technical documentation. Interoperability with gLite storage element is provided by an other set of ARC library. This data library provides native interfaces to GridFTP\cite{gridftp} SRM which is the main bulding blocks of a gLite storage element. A storage interopability is out of scope of this library.

@@

An overview of the preferred soulution is presented in figure \ref{fig:Chart 1}. The user will be able to express his requirements in the job description document using any of the xRSL\cite{xrsl}, JDL or JSDL\cite{jsdl} languages. The ARC client library will perform an automatic transformation. The gLite gateway functionality integrated into the ARCLIB, thus into the ARC client enables the user to transparently access gLite computing resources via the usual ARC command line tools. The gLite modules perform authentication, credential delagation and job submission to the CREAM2 CE. The CREAM2 CE may perform the necessary input file download from the different storage element. The library module gets job information through CREAM2 and sends management commands, like kill a job or undelegate credentials. Note, that not all the functionality described on the overview figure is implemented yet, for the current limitations see section \ref{Current limitations}!\par

@@

The gLite computing element (CE) offers several interfaces. Some of them are only suitabe for the WMS (glite resource broker) and was not meant to be used by 3rd party clients. Fortunately gLite comes with a webservice based computing element interface, known as the CREAM CE. The CREAM has undergone several major revisions. We can only hope that some stability will soon arise. The current CREAM version has entered the EGEE certification process newertheless it is a full scale deplomeyment on the EGEE worldwide grid has not taken place yet. CREAM2 is available on several preproduction and testing grid sites.\par
Nevertheless the KnowARC project chose the CREAM version 2\cite{cream} as the gLite computing element interface.\par

@@

\item Unlike the other gLite CE interfaces it supports direct job status queries 

@@

In the near future CREAM will offer yet another interface which will be based on the BES/JSDL/GLUE OGF standards. This CREAM BES interface will coexists with the CREAM2 too.\par

@@

The ARCLIB gLite plugins have only one dependency. GridFTP components of the Globus Toolkit\cite{globus} are needed to enable data staging functionality to those CREAM2 computing elements which offer input and output sandbox over a GridFTP enabled storage. Unfortunately the gateway library only works together with a strongly patched Globus verion. The NorduGrid patched Globus can be dowloaded from the NorduGrid download area\footnote{\url{http://download.nordugrid.org/software/globus/}}. Further information about the NorduGrid Globus patches can be read on the NorduGrid page\footnote{\url{http://wiki.nordugrid.org/index.php/Globus\_Libraries}}. It is worth to mention that the user will need a VOMS\cite{voms} proxy certificate in order to use the command line tools against a CREAM2 service. This VOMS proxy can be generated by using the VOMS client tools. It is only the VOMS enabled proxy certificate that is needed here, appart from this no VOMS component needed.\par
The ARC gLite gateway plugins library and the temporary command line utilities are incorporated into ARC1 releases. The source code is available from the ARC1 SVN repository\footnote{\url{http://svn.nordugrid.org/repos/nordugrid/arc1/}} and binary packages are provided at the NorduGrid download area. The build and installation instructions are given in the README file distributed together with the software. A step-by-step guide for Debian binary installation can be found in the appendix \ref{Debian install} \textit{Installation from Debian binary packages}.

@@

The ARCLIB gLite gateway plugins constist of the wrapper classes, the job description handling facility and the gLite specific CREAMClient base class. The wrapper classes coveys the function provided by the CREAMClient to ARCLIB. The job description handling framework makes a general job request representation available for the other classes. CREAMClient base class implements the interface towards CREAM2 computing elements.
This client object has an easy-to-use and intuitive interface. It uses the VOMS proxy certificate to build the secure channel to the server and to sign that of the server's.

@@

... mik ezek a wrapper osztályok ... milyen base class, mit csinál, mi a funckiójuk ... viszonylag részletesen ...

@@

... Bárhol meghívható ... objektumot példányosítani ... milyen transzformációk állank rendelkezésre ...

@@

The client object uses the VOMS proxy certificate to build the secure channel to the server and to sign that of the server's.\par
... 1 bekezdés arról, hogy SOAP a hed(Hivatkozni!!!) SOAP framework-jét használja 'fully integrated'... az előző deliverable-ben a kommunikáció gSOAP-ot használt, ez az egyik nagy előrelépés, hogy ezt lecseréltük...\cite{gsoap}... 
\subsubsection*{CREAMClient(Arc::URL, Arc::MCCConfig)}

@@

Besides the constructor this is the other generic-purpose function that can be used in CREAM2 client applications. This function sets the previously registered and referred delegation ID on the client. The function is very simple: just set a private variable and returns with no value.

@@

This method has the reverse functionality of the \textbf{createDelegation} function. It sends the \textit{destroy} message of CREAM2 to the remote server.

@@

The \textbf{submit} function is the most complex part of the class. It translates the job description received as the argument, registers the job with a \textit{JobRegisterRequest} message, uploads the locally stored files, if necessary, then enables the job execution on the server by sending a \textit{JobStartRequest} message. Finally it returns with a \textbf{creamJobInfo} object that contains a \textit{jobId} (job indetifier), a \textit{creamURL} (as the service URL), an \textit{ISB} (reference to the Input Sandbox) and an \textit{OSB} (Output Sandbox) member to describe the registered job. In the \textbf{glitesub} command (See Section \ref{glitesub} for details) these pieces of information are stored in the information file.

@@

Unfortunately the interoperability features offered by the gLite gateway library are not yet integrated into the NorduGrid commands. Also the current version of ARCLIB does not offer the full spectrum of language transformations.
However only a set of temporary command line tools exposing the available features of library are provided. These temporary commands make the already existing interoparabilily features usable for ordinary users.
There are seven different command line tools for using the gLite gateway functions. In this section these tools will be presented in detail through examples. The job descriptions and services shown are just simple examples, they might be different in real-life usage.\par

@@

The usage of command \textbf{glitedelegate} is straighforward. All needed is a working CREAM2 delegation service URL, and a locally unique arbitrary delegation ID. This delegation ID will be associated to the remote resource. If you are not sure wether your favourite delegation ID is occupied or not, then try to delete it before registering it again. (See Section \ref{gliteundelegate} for further details!) The delegation command has the following syntax:

@@

The current command only supports direct job submission that is the user must know service endpoints. These kind of endpoints usually stored in LDAP databases. Ordinary ldapsearch can be used to find such an endpoint. Below an example:\par

@@

The \textbf{glitesub} command requires a valid delegation. See Section \ref{glitedelegate} how to create one. By the way this is the only command which needs the delegation ID.\par The next step is to prepare the necessary input files and the job description!\par

@@

Here the delegation ID is the identification registered previously. The service URL will be different than in the delegation example above, because this is not the URL of the delegation, but the execution service. The job description must be in JDL format like in the example below. The info file stores information about the job submitted. It should either be a non-existing file otherwise it is overwritten. This file contains the job ID, the input sandbox URL, the output sandbox URL and the service URL.\par

@@

... mit csinál a parancs sikeres és sikertelen futás esetén... \par

@@

After the work is complete it is possible to unregister and delete the delegation entry from the remote site by using command \textbf{gliteundelegate}. It can also be used when one needs to register a delegation ID but are unsure whether it is already used or not. Put the delegation delegation service URL into the argument!\par

@@

It is of course mandatory to define \textit{SERVICE\_URL} and \textit{JOBID} strings to their real values to reach the proper functionality.

@@

In order to achieve the full scale transparent interoperability width the gLite computing element transparently offered through the NorduGrid client a couple of issues still need to be resolved. Most of these are related to the incomplete integration of the glite gateway library into the ARCLIB framework, even though the gateway library code is ready for production use. There are also some conceptual chanlenges due to the incompatible nature of the two systems which require development of some workarounds.

@@

Full ARC1 client integration would mean that the temporary commands developed on top of the CREAMClient\ref{CREAMClient} presented in the previous section will be obsoleted by the ordinary ARC commands built on top of the ARCLIB. To achieve this the Wrapper class integration of the gLite gateway plugins library should finalized and exposed to extended testing.\par

@@

The CREAMClient class will be extended to support operations such as SUSPEND available both in the CREAM2 interface and the ARCLIB's jobcontrol component.\par
Due to the incomplete ARCLIB integration currently only direct job submission to a manually selected CE is possible. The ARCLIB integration will combine the existing resource discovery (REF ... a Wrapperre) and job submission functionality (REF ... a Wrapperre)  of the glite gateway plugins with the brokering module of ARCLIB, which is  currently under development. The combination of these ARCLIB modules will provide intelligent brokered job submission over glite and nordugrid computing element.\par
For a fully transparent integration the automatic translation among JSDL/XRSL and JDL should also be provided. A user should be able to specify his/her job request in any of these languages and the gateway do the necessary translations.  The current language translator module currently is not capable generating JDL output.  Therefore, the user still needs to use JDL if he/she wants to submit jobs to CREAM2.\par
Further investigation is needed how a CREAM2 service handles data staging and whether the data movement related ARC libraries can be used to manage data staging in the client side or development of special data staging wrapper scripts to be executed on the computing element are needed.
A set of temporary workaround command line clients had to be developed (the glite* commands [... REF]) due to a discovered OpenSSL version conflict. The conflict appeared when we tried to integrate the CREAMClient gateway library with the rest of the ARCLIB. A tedious and time consuming debugging process took place. The debugging revealed the following:  A VOMS proxy certificate delegation method was implemented in the CREAMClient gateway library. During this process it was needed to sign a certificate and the original OpenSSL was used for this purpose. In the used communication library taken from the ARC1 framework there is a built-in Message Chain Component (MCC) which already utilizes the Globus Toolkit OpenSSL functions to enable establishing secure communication. Linking the CREAMClient library directly against the standard OpenSSL libs caused congesting SSL functions.  In order to resolve the OpenSSL conflict and to make possible the complete ARCLIB integration  a globus patch has been being worked on. Once the OpenSSL conflict is resolved the ARCLIB integration will be completed this way obsoleting the glite* temporary commands.\par

@@

During the development of the gateway library a few conceptual incompatibilities were found.  These are the typical cases when one of the middlewares offers richer capabilities not available in the other one. These conceptual gaps can only be bridged by developing customized case by case workarounds, nevertheless  the interoperation always would result in some information loss in these cases.\par
Below we collected the most important challenges for which we still have to find some solution:

@@

XRSL  offers reacher capability to describe input and output date of a job than the JDL.  Speciﬁcally, in xRSL it is possible for input files downloaded from storage servers to have their names changed. This is not possible in JDL. So a user might in xRSL ask for this:

@@

That is not possible to express in JDL. It only allows the file to be downloaded as datafile1.txt. This could be solved by a wrapper script that renames files according to the xRSL speciﬁcation. This does not solve our problem completely however. For example if a user wants to concatenate the stdout from two jobs, he would write something like the following in xRSL:

@@

This cannot be solved just using the renaming method, because both input files would be retrieved before renaming is done and they would therefore overwrite each other.\par

@@

Many grid jobs rely on software being available at the execution location. The requirement as well as the initialization of such software is expressed through the use of Run-Time Environments (RTEs). While the library is capable of translating the RTE request itself it is not capable of translating the name of the RTE. No standardized cross Grid nomenclature has been adopted, nor are the authors aware of any such activity. A temporary solution would be to have a remotely accessible list of RTEs and their names in each job description language. This could then be used for translating jobs.

@@

\item Put the Debian repository into the APT source files (/etc/apt/sources.list). This repository in Luebeck is maintained as long as the KnowARC procject continues.

@@

\item Create the vomses file:

>>>>

\def\documenttitle{The gLite gateway plugins of ARCLIB and related command line tools}
\captionsetup{margin=20pt,font={footnotesize, it},labelfont=bf}
\begin{document}
\def\today{\number\day/\number\month/\number\year}
\begin{titlepage}

@@

{\raggedleft NORDUGRID-TECH-22\par}

@@

The purpose of this document is to describe this gLite\cite{glite} specific plugins of the ARCLIB\cite{arclib} to present the related command line utilities built on top of these libraries. The gateway library together with the tools enables seemless interoparability with gLite computing elements. It is possible, that relevant sections of this document will be moved into ARC1 userguide and into ARCLIB technical documentation. Interoperability with gLite storage element is provided by an other set of ARC library. This data library provides native interfaces to GridFTP\cite{gridftp} SRM which is the main bulding blocks of a gLite storage element. A storage interopability is out of scope of this library.

@@

An overview of the preferred soulution is presented in figure \ref{fig:Chart 1}. The user will be able to express the job requirements in the job description document using any of the xRSL\cite{xrsl}, JDL or JSDL\cite{jsdl} languages. The ARC client library will perform an automatic transformation. The gLite gateway functionality integrated into the ARCLIB, thus into the ARC client allow the user to transparently access gLite computing resources via the usual ARC command line tools. The gLite modules perform authentication, credential delagation and job submission to the CREAM2 CE. The CREAM2 CE may perform the necessary input file download from the different storage elements. The library module gets job information through CREAM2 and sends management commands, like kill a job or undelegate credentials. Note that not all the functionality described in the overview figure is implemented yet, for the current limitations see section \ref{Current limitations}!\par

@@

The gLite computing element (CE) offers several interfaces. Some of them are only suitabe for the WMS (gLite resource broker) and was not meant to be used by 3rd party clients. Fortunately gLite comes with a webservice based computing element interface, known as the CREAM CE. The CREAM has undergone several major revisions. The current CREAM version has entered the EGEE certification process nevertheless it is a full scale deplomeyment on the EGEE worldwide grid has not taken place yet. CREAM2 is available on several preproduction and testing grid sites, KnowARC has chosen the CREAM version 2\cite{cream} as the gLite computing element interface.\par

@@

\item Unlike the other gLite CE interfaces it supports direct job status queries.

@@

In the near future CREAM will offer yet another interface which will be based on the BES/JSDL/GLUE OGF standards. This CREAM BES interface will coexists with CREAM2 too.\par

@@

The ARCLIB gLite plugins have only one dependency. GridFTP components of the Globus Toolkit\cite{globus} are needed to enable data staging functionality to those CREAM2 computing elements which offer input and output sandbox over a GridFTP enabled storage. Unfortunately the gateway library only works together with a strongly patched Globus verion. The NorduGrid patched Globus can be dowloaded from the NorduGrid download area\footnote{\url{http://download.nordugrid.org/software/globus/}}. Further information about the NorduGrid Globus patches can be read on the NorduGrid page\footnote{\url{http://wiki.nordugrid.org/index.php/Globus\_Libraries}}. It is worth to mention that the user will need a VOMS\cite{voms} proxy certificate in order to use the command line tools against a CREAM2 service. This VOMS proxy can be generated by using the VOMS client tools. It is only the VOMS enabled proxy certificate that is needed here, apart from this no VOMS components are needed.\par
The ARC$\rightarrow$gLite gateway plugins library and the temporary command line utilities are incorporated into ARC1 releases. The source code is available from the ARC1 SVN repository\footnote{\url{http://svn.nordugrid.org/repos/nordugrid/arc1/}} and binary packages are provided at the NorduGrid download area. The build and installation instructions are given in the README file distributed together with the software. A step-by-step guide for Debian binary installation can be found in appendix \ref{Debian install} \textit{Installation from Debian binary packages}.

@@

The ARCLIB gLite gateway plugins constist of the wrapper classes, the job description handling facility and the gLite specific CREAMClient base class. The wrapper classes covey the function provided by the CREAMClient to ARCLIB. The job description handling framework makes a general job request representation available for the other classes. CREAMClient base class implements the interface towards CREAM2 computing elements.
This client object has an easy-to-use and intuitive interface. It uses the VOMS proxy certificate to build the secure channel to the server and also to sign that of the server's.

@@

\label{Wrapper classes}
The gLite gateway library can be integrated into the ARCLIB as a plugin. To expose the CREAM2 functionality into the generic ARCLIB target object functions, the following three wrapper classes have been implemented: the JobController, the Submitter and the TargetRetriever.\par
The JobControllerCREAM wrapper class provides the basic functions related to job management, such as getting job information or killing and cleaning the job on the remote CE.\par
The SubmitterCREAM instantiates the gLite client library and calls the CREAM2-specific submitter function in there.\par
Class TargetRetrieverCREAM performs a BDII database query and extracts the possible CREAM2 target objects.\par
Unfortunately handling CREAM2 target objects do not perfectly fit into the philosophy of ARCLIB, there are several functions, such as proxy credential delegation or CREAM2-specific job information retrieval that behaves differently on an ARC1 and on a CREAM2 target. The wrapper classes have to provide solutions for these special cases.

@@

\label{Job description}
When addressing interoperability it is of paramount importance to transparently address grid job descriptions written in different job description languages by translating them automatically. In the gLite gateway library code this functionality is implemented in class JobDescription. This is a generic class that takes a job description as input in any supported formats (currently xRSL, JDL, JSDL), converts and stores it in a JSDL-like internal job description format. Then different operations, like getting the description in other formats or getting job-related information, can be performed using the description-independent functions of this class.\par
JobDescription has tree back-end classes, sometimes are referred to as back-end modules or translator modules, corresponding to the three supported job description languages above. The back-end classes are used for parsing and also for generating the job descriptions. These classes do not store information and are not intended to be used directly, instead, the generic class uses them.\par
There is a class called JobDescriptionOrderer which tries to find out the format of the input file by pattern matching; the generic class uses this piece of information to choose the appropriate back-end.
\centering{\resizebox{255px}{!}{\includegraphics{JobDescriptionExample-XRSLInput.jpg}}
\caption{\label{fig:Chart 1}The figure shows how the different classes participating in the job description translation process interrelate in an example about xRSL parsing.}}

@@

The client object uses the VOMS proxy certificate to build the secure channel to the server and also to sign that of the server's.\par
To establish the SOAP connection via the secure channel, the library use the native ARC1 HED\footnote{\url{https://www.knowarc.eu/documents/Knowarci\_D1.1-1\_07.pdf}} Message Chain Component (MCC), that provides full integration with the ARC1 core and corresponding services. This replaced the former gSOAP-based\cite{gsoap} communication libraries, which enabled the full elimination of the gSOAP dependency.
\subsubsection*{CREAMClient(Arc::URL, Arc::MCCConfig)\footnote{For class references see: \url{https://www.knowarc.eu/download/D1.2-2\_documentation.pdf}}}

@@

Besides the constructor this is the other generic-purpose function that can be used in CREAM2 client applications. This function sets the previously registered and referred delegation ID on the client. The function is simple: it sets a private variable and returns with no value.

@@

This method has the reverse functionality of function \textbf{createDelegation}. It sends the \textit{destroy} message of CREAM2 to the remote server.

@@

The \textbf{submit} function is the most complex part of the class. It translates the job description received as the argument, registers the job with a \textit{JobRegisterRequest} message, uploads the locally stored files, if necessary, then launches the job execution on the server by sending a \textit{JobStartRequest} message. Finally it returns with a \textbf{creamJobInfo} object that contains a \textit{jobId} (job indetifier), a \textit{creamURL} (as the service URL), an \textit{ISB} (reference to the Input Sandbox) and an \textit{OSB} (Output Sandbox) member to describe the registered job. In the \textbf{glitesub} command (See Section \ref{glitesub} for details) these pieces of information are stored in the information file.

@@

Unfortunately the interoperability features offered by the gLite gateway library are not yet integrated into the NorduGrid commands. Also the current version of ARCLIB does not offer the full spectrum of language transformations.\par
However only a set of temporary command line tools exposing the available features of the library are provided. These temporary commands make the already existing interoparabilily features usable for ordinary users.\par
There are seven different command line tools for using the gLite gateway functions. In this section these tools will be presented in detail through examples. The job descriptions and services shown are just simple examples, their arguments might be different in real-life usage.\par

@@

The usage of command \textbf{glitedelegate} is straighforward. All needed is a working CREAM2 delegation service URL, and a locally unique arbitrary delegation ID. This delegation ID will be associated to the remote resource. If you are not sure whether your favourite delegation ID is occupied or not, then try to delete it before registering it again. (See Section \ref{gliteundelegate} for further details!) The delegation command has the following syntax:

@@

The current command only supports direct job submission that is the user must know service endpoints. These kind of endpoints usually stored in LDAP databases. Ordinary ldapsearch can be used to find such an endpoint. Below comes an example:\par

@@

The \textbf{glitesub} command requires a valid delegation. See Section \ref{glitedelegate} how to create one. By the way this is the only command which needs the delegation ID.\par The next step is to prepare the necessary input files and the job description.\par

@@

Here the delegation ID is the identification registered previously. The service URL will be different than in the delegation example above, because this is not the URL of the delegation, but the execution service. The job description must be in JDL format like in the example below. The info file stores information about the job submitted. It should be a non-existing file otherwise it will be overwritten. This file contains the job ID, the input sandbox URL, the output sandbox URL and the service URL.\par

@@

After successful completion the command reports the success and tells the user where the job related data are stored. Otherwise the message written to the output contains the reason of the failure.

@@

After the job execution is complete it is possible to unregister and delete the delegation entry from the remote site by using command \textbf{gliteundelegate}. It can also be used when one needs to register a delegation ID but is unsure whether it is already used or not. Put the delegation service URL into the argument!\par

@@

It is of course mandatory to set \textit{SERVICE\_URL} and \textit{JOBID} strings to their real values to obtain the proper functionality.

@@

In order to achieve the full scale transparent interoperability width the gLite computing element transparently offered through the NorduGrid client a couple of issues still need to be resolved. Most of these are related to the incomplete integration of the gLite gateway library into the ARCLIB framework, even though the it is ready for production use. There are also some conceptual challenges due to the incompatible nature of the two systems, which requires workarounds.

@@

\label{Current limitations}
Full ARC1 client integration would mean that the temporary commands developed on top of the CREAMClient presented in the previous section \ref{CREAMClient} will be overriden by the ordinary ARC commands built on top of the ARCLIB. To achieve this the Wrapper class integration of the gLite gateway plugins library should be finalized and exposed to extensive testing.\par

@@

The CREAMClient class will be extended to support operations such as \textit{suspend} available both in the CREAM2 interface and the ARCLIB's jobcontrol component.\par
Due to the incomplete ARCLIB integration currently only direct job submission to a manually selected CE is possible. The ARCLIB integration will combine the existing resource discovery (See section \ref{Wrapper classes}) and job submission functionality of the gLite gateway plugins with the brokering module of ARCLIB, which is  currently under development. The combination of these ARCLIB modules will provide intelligent brokered job submission over gLite and NorduGrid computing element.\par
For a fully transparent integration automatic translation among JSDL/xRSL and JDL should also be provided. A user should be able to specify his/her job request in any of these languages and the gateway does the necessary translations.  The current language translator module currently is not capable of generating JDL output.  Therefore, the user still needs to use JDL to submit jobs to CREAM2.\par
Further investigation is needed on how a CREAM2 service handles data staging and whether the data movement related ARC libraries can be used to manage data staging on the client side or development of special data staging wrapper scripts executed on the computing element are needed.
A set of temporary workaround command line clients have been developed (the glite* commands; see section \ref{Users guide}) due to a discovered OpenSSL version conflict. The conflict appeared when we tried to integrate the CREAMClient gateway library to the rest of the ARCLIB. A tedious and time consuming debugging process took place. It revealed the following:  A VOMS proxy certificate delegation method was implemented in the CREAMClient gateway library. During this process it was needed to sign a certificate and the original OpenSSL was used for this purpose. In the communication library used and taken from the ARC1 framework there is a built-in Message Chain Component (MCC) which already utilizes the Globus Toolkit OpenSSL functions to enable establishing secure communication. Linking the CREAMClient library directly against the standard OpenSSL libs caused congesting SSL functions.  In order to resolve the OpenSSL conflict and to make possible the complete ARCLIB integration  a Globus patch has been worked out. Once the OpenSSL conflict is resolved the ARCLIB integration will be completed this way overriding the temporary glite* commands.\par

@@

During the development of the gateway library a few conceptual incompatibilities were found. These are the typical cases when one of the systems offers richer capabilities not available on the other one. These conceptual gaps can only be bridged by developing customized case by case workarounds, nevertheless  the interoperation always would result in some information loss in these cases.\par
Below are the most important challenges for which solution is still sought:

@@

The xRSL offers richer capability to describe input and output date of a job than JDL. Especially, in xRSL it is possible for input files downloaded from storage servers to have their names changed. This is not possible in JDL. So in xRSL user might ask for this:

@@

That is not possible to express in JDL. It only allows the file to be downloaded as datafile1.txt. This could be solved by a wrapper script that renames files according to the xRSL speciﬁcation. This does not solve the problem completely however. For example if a user wants to concatenate the stdout from two jobs, he would write something like the following in xRSL:

@@

This cannot be solved just using the renaming method, because both input files would be retrieved before the renaming and they would therefore overwrite each other.\par

@@

Many grid jobs rely on software being available at the execution location. The requirement as well as the initialization of such software is expressed through the use of Run-Time Environments (RTEs). While the library is capable of translating the RTE request itself it is not capable of translating the name of the RTE. No standardized cross-grid nomenclature has been adopted, nor are the authors aware of any such activity. A temporary solution would be to have a remotely accessible list of RTEs and their names in each job description language. This could then be used for translating jobs.

@@

\item Put the Debian repository into the APT source files (/etc/apt/sources.list). This repository in Luebeck is maintained as long as the KnowARC project continues.

@@

\item Create the vomses directory
